descriptive_Clusters

### 2020-12-03 src/descriptive_Clusters.Rmd

@@

@@

cluster.up <- cluster.up[which(cluster.up$up.LADs > 5),]

@@

UpCluster <- ggplot(cluster.up, aes(help.date.time, mean.up, 

@@

UpCluster + geom_line() + labs(x = "Weekdays March-May") + 

>>>>

#create time variation plots for speedtests for each year
Tests19 <- count(TS2019, date)
TS2019 <- left_join(TS2019, Tests19)
names(TS2019)[13] <- "test frequency 2019"
timeVariation(TS2019, pollutant = "test frequency 2019", statistic = "mean")
Tests20 <- count(TS2020, date)
TS2020 <- left_join(TS2020, Tests20)
names(TS2020)[13] <- "test frequency 2020"
timeVariation(TS2020, pollutant = "test frequency 2020", statistic = "mean")

@@

#plot largest 5 clusters first - all over 1 million pop

@@

cluster.up <- cluster.up[which(cluster.up$up.LADs > 9),]

@@

UpClusterL <- ggplot(cluster.up, aes(help.date.time, mean.up, 

@@

UpClusterL + geom_line() + labs(x = "Weekdays March-May", y = "mean upload speed") + 
#plot next 6 smaller clusters, but exclude 2 clusters with 1 LAD and under 100k pop
cluster.upS <- TS2020 %>%
names(cluster.upS)[1] <- "clusterID"
cluster.upS <- left_join(cluster.upS, LAD.cluster.up)
cluster.upS <- cluster.upS[which(cluster.upS$up.LADs < 10 & cluster.upS$up.LADs > 1),]
cluster.upS$clusterID <- as.factor(cluster.upS$clusterID)
cluster.upS <- merge(cluster.upS, help.dates, by = "weekday")
cluster.upS$hour <- paste(cluster.upS$hour, ":00", sep="")
cluster.upS$help.date.time <- with(cluster.upS, as.POSIXct(paste(help.date.time, hour), format="%Y-%m-%d %H:%M"))
UpClusterS <- ggplot(cluster.upS, aes(help.date.time, mean.up, 
UpClusterS + geom_line() + labs(x = "Weekdays March-May", y = "mean upload speed") + 
